Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-05-25 manuscript/manuscript.Rmd
rewrites from PBA suggestions

**5.** *Synthesis.* For our focal species at this particular location, and using our particular statistical models, demographic data was generally unnecessary to achieve skillful [ARE ANY OF THESE FORECASTS SKILLFUL? FOCUS INSTEAD ON MODEL DIFFERENCES] forecasts, though for certain species forecast skill can be gained by using demographic data linked to climate covariates.
We conclude that models based on aggregated individual-level data offer a practical alternative to data-intensive demographic models when species do not respond strongly to interannual variation in weather, but when modeling species that do respond to climate drivers, demographically-based models can generate more skillful forecasts.

@@

<!--
The inability of most population models to address landscape-scale problems may explain why land managers and conservation planners have embraced species distribution models (SDMs) [see @Guisan2005 for a review]. SDMs typically rely on easy-to-collect presence/absence data and remotely-sensed environmental covariates that allow researchers to model large spatial extents [e.g., @Maiorano2013]  and project future changes in occupancy over landscapes and regions. However, the limitations of SDMs are well known [@Pearson2003; @Elith2009; @Araujo2012]. Ideally, researchers would provide managers with landscape-scale population models, combining the extent of SDMs with information about dynamics and species abundances [@Schurr2012; @Merow2014].  
-->

@@

Addressing climate change questions with models fit to population-level data is potentially problematic.  Population growth (or decline) is the outcome of demographic processes such as survival, growth, and recruitment that occur at the level of individual plants. Climate can affect each demographic process in unique, potentially opposing, ways [@Dalgleish2011]. These unique climate responses may be difficult to resolve in statistical models based on population-level data where demographic processes are not identifiable. Futhermore, models based on aggregated data may reflect short-term effects of one vital rate more than others whose importance may only emerge over the long-term. For example, a one-year change in a plant species' cover or biomass might reflect individual growth or shrinkage, whereas the long-term trajectory of the population might be more influenced by recruitment.  If important climate effects are missed because of the aggregation inherent in in population-level data, then population models built with such data will make uninformative or unreliable forecasts.

Here, we compare the forecasting skill of statistical and population models based on aggregated, population-level data with the skill of models based on individual-level data. We used a demographic dataset that tracks the fates of individual plants from four species over 14 years to build two kinds of single-species population models, traditional models using individual growth, survival, and recruitment data and alternative models based on basal cover. We simulated the models to answer two questions: (1) Can population models fit using aggregated individual-level data (percent cover) adequately capture density dependence to produce forecasts as skillful as those from models fit to demographic data? 
(2) Can population models fit using aggregated data adequately capture the influence of climate on population growth and, in turn, produce forecasts as skillful as those from models fit to demographic data? 
[THIS NEXT SENTENCE SEEMS OUT OF PLACE. CAN YOU MODIFY PREVIOUS PARAGRAPH TO ADDRESS DENSITY DEPENDENCE ALONG WITH CLIMATE EFFECTS? E.G. DENSITY DEPENDENCE MIGHT ACT MOST STRONGLY ON RECRUITMENT WHICH IS HARD TO DETECT IN A COVER BASED MODEL?] Both questions are motivated by the fact that the effects of intraspecific competition (density dependence) and interannual weather variability act at the level of the individual [@Clark2011b], meaning that models based on individual-level processes should generate more skillful forecasts.

@@

YOU NEED TO EXPLAIN HOW THE w's ARE CALCULATED. COPY TEXT FROM ADLER ET AL. 2010 or CHU  & ADLER 2015.

@@

This cross-validation procedure allowed us to compare accuracy and precision of the two modeling approaches (IPM versus QBM) with and without climate covariates. We first calculated the median predicted cover across the 100 simulations for each quadrat-year and then calculated forecast skill as the correlation ($\rho$) between forecasts and observations. We compared $\rho$ between model types and within model types between models with and without climate covariates using a one-sided *t* test with adjusted degrees of freedom following @Wilcox2009 and standard errors calculated using the HC4 estimator of @Cribari-Neto2004. Statistical tests for differences between $\rho$ were conducted using R functions from @Ye2015a.

@@

<!--
### Testing sensitivity to climate covariates
With our fitted and validated models in hand, we ran simulations for each model type (IPM and QBM) under four climate perturbation scenarios: (1) observed climate, (2) precipitation increased by 1%, (3) temperature increased by 1%, and (4) precipitation and temperature increased by 1%. We ran the simulations for 2,500 time steps, enough to estimate equilibrium cover after discarding an initial 500 time steps as burn-in. EXPLAIN HOW CLIMATE COVARIATES ARE DRAWN AT EACH TIME STEP. AND NO RANDOM YEAR EFFECTS? Each simulation was run under two parameter scenarios: (1) using mean parameter estimates and (2) using randomly drawn parameters from the MCMC chain. We use (1) to detect the overall sensitivity of equilibrium cover to climate, and we use (2) to show the impact of model and parameter uncertainty on forecast precision.

As an effort to identify potential discrepencies between IPM and QBM forecasts, we also ran simulations designed to quantify the sensitivities of individual and combined vital rates to climate for the IPM. Specifically, we ran simulations for the above climate scenarios, but applied the perturbed climate covariates to survival, growth, or recruitment vital rates individually and in pairwise combinations. This allowed us to isolate the vital rate(s) most sensitive to climate. For this analysis, we used mean parameter estimates to reduce the sources of uncertainty in the sensitivity estimates.

We expected the IPM to produce more accurate and precise forecasts due to either (1) the smaller sample size of the quadrat level data sets compared to the individual level data sets, leading to larger parameter uncertainty for the QBM, or (2) the QBM climate effects being weakly associated with one or more vital rate climate effects at the individual level. To assess the impact of sample size on QBM parameter uncertainty, we refit the QBM statistical model (Eqs. 9-10) after removing sets of 2, 5, 10, and 15 quadrats. We fit 10 models at each level of quadrat removal (2, 5, 10, 15 quadrats), removing a different randomly selected set of quadrats for each fit. We calculated the standard deviation of climate main effects (pptLag, ppt1, ppt2, TmeanSpr1, and TmeanSpr2) for each model and averaged those over replicates within each set of quadrat removals. This allowed us to regress parameter uncertainty against sample size.

To deterime if the QBM climate effects are correlated with climate effects for each vital rate model in the IPM, we simply regressed the QBM climate coefficients against each vital rate model's climate coefficients and calculated Pearson's $\rho$. Strong correlations indicate the QBM is capable of detecting climate effects associated with individual vital rates. A weak correlation indicates the QBM "misses" the climate effect on a particular vital rate.
-->

Results
-------
Both the IPM and QBM generated skillful one-step-ahead forecasts for out-of-sample observations, with an average correlation between predictions and observations ($\rho$) of 0.73 across all models and species (Fig. 2). IS THIS SKILLFUL FORECASTING OR IS THIS JUST STRONG AUTOCORRELATION IN COVER?
Without climate covariates, the accuracy of forecasts from the IPM were not statistically greater than the accuracy of forecasts from the QBM (Fig. 2) and overall error was similar (mean absolute error; Fig. S1).
With climate covariates, the best out-of-sample predictive model (highest *lppd*) for each species and vital rate typically resulted from highly constrained priors on the climate effects (Fig. S2).
Thus, the posterior distributions of climate effects included in our models overlapped zero and generally shrunk toward zero, though for some species-vital rate combinations important effects (80% credible interval does not include zero) did emerge (Fig. 3).

Despite the weak climate effects, including climate covariates did increase the accuracy of forecasts for all species except *P. smithii* (Fig. 2).
Increases in accuracy due to the inclusion of climate covariates were not significant (*P* > 0.05 for all comparisons of $\rho$ between climate and no-climate forecasts within model types; Fig. 2).
PREVIOUS SENTENCE READS AS INCONSISTENT WITH NEXT SENTENCE.
However, the IPM with climate covariates for *P. secunda* did have significantly lower error than the IPM without climate covariates ($t_{(196)}$ = -1.84, *P* = 0.033; Fig. S2).
In only one case were IPM forecasts significantly more accurate than the QBM (Fig. 2): forecast accuracy of *P. secunda* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(195)}$ = 1.72, *P* = 0.043).
WHAT IS THE DIFFERENCE BETWEEN ACCURACY (PREVIOUS SENTENCE) AND ERROR (NEXT SENTENCE)?
Forecasts from IPMs with climate covariates had significantly lower error than equivalent QBM forecasts for *P. smithii* ($t_{(216)}$ = -3.49, *P* < 0.001) and *P. secunda* ($t_{(196)}$ = -1.83, *P* = 0.034) (Fig. S2).
Results from all pairwise statistical tests are shown in Table S1.

The accuracy of both model's forecasts declined as the forecast horizon increased, but they did so at similar rates (Fig. 4).
The only exception is for *P. secunda* where forecast accuracy appears to slightly increase with forecast horizon, after an initial decrease from a forecast horizon of one year (Fig. 4).

I TRIED TO BREAK THIS PARAGRAPH UP TO MAKE RESULTS EASIER TO FOLLOW

IS THIS NEXT PART OLD?

<!--
### Comparison of forecast models

### Sensitivity of models to climate
The response of a population to climate change is a result of the aggregate effects of climate on individual vital rates. Since the IPM approach relies on vital rate regressions, we were able to quantify the sensitivity of each vital rate in isolation and in pairwise combinations. Across all species, climate covariates often had opposing effects on different vital rates (Fig. 3). Growth was the most sensitive vital rate for all species, showing a negative response to increased precipitation, and stronger positive response to increased temperature, and a mostly positive response when both climate factors were increased (Fig. 3). *B. gracilis* survival rates were sensitive to temperature, resulting in an increase in plant cover under increased temperature (Fig. 3a). Recruitment and survival were insensitive to climate factors for *H. comata* (Fig. 3b). Survival and recruitment of *P. smithii* were both sensitive, negatively, to temperature and precipitation (Fig. 3c). *P. secunda* equilibrium cover was sensitive to the climate effects on survival and recruitment, showing a negative effect on both vital rates for increased precipitation, but a positive effect on survival with increased temperature (Fig. 3d). Equilibrium cover OF WHICH SPECIES? responded negatively when increased precipitation and temperature affected recruitment  (Fig. 3d). At least two of three vital rates were sensitive to climate for each species (Fig. 3). BY WHAT CRITERIA? FIG 3 SHOWS ONLY ONE COLORED RESPONSE FOR TWO SPECIES, AND NONE FOR POA.

### Sources of uncertainty in the QBM
Sample size had a relatively weak effect on QBM climate parameter uncertainty when more than 10f quadrats were used in fitting (Fig. 5). Based on inverse-gaussian fits, increasing sample size beyond the number of quadrats we used would result in diminishing returns in terms of parameter certainty (Fig. 5).

Climate effects estimated from the QBM were most correlated with climate effects from the growth regression at the individual level (Fig. 6). In no case did the QBM statistical model have strong correlations across all three vital rates (Fig. 6). QBM climate effects were most weakly correlated with those from individual-level recruitment models for *B. gracilis*, *H. comata*, and *P. secunda* (Fig. 6a,b,d). For *P. smithii*, QBM climate effects showed no correlation with the survival model effects (Fig. 6c).

### Model forecasts
Forecasts of changes in equilibrium cover in response to 1% climate perturbations were extremely uncertain when we considered model error and parameter uncertainty (Fig. 6; simulations with mean parameters are in Appendix D for comparison). Consistent with the model validation results (Table 1), QBM projections were more uncertain than IPM projections for all species except *P. smithiii* (Fig. 6). IPM forecasts for *P. smithiii* were very uncertain due to a very high intrinsic rate of recruitment combined with uncertainty in climate coefficients which led to  boom years in recruitment and subsequent busts when small plants suffered high mortality (Appendx C). When we included model error and parameter uncertainty, forecast changes in proportional cover always spanned a wide range of negative to positive values. In other words, neither model could predict whether a climate perturbation would increase or decrease equilibrium population size.
-->

@@

Our comparison of a traditional, demographic population model without environmental forcing (the IPM) to an equivalent model inspired by density-structured models (the QBM) showed that, generally, IPM forecasts of out-of-sample plant population states were no more accurate than forecasts from the QBM (Fig. 2; `no-climate' bars).
We expected the IPM to out-perform the QBM since the IPM includes more mechanistic detail on the perennial plant life cycle, but this was not the case, at least when we ignored environmental forcing.
Such a finding confirms theoretical [@Freckleton2011] and empirical work [@Queenborough2011] showing that density-structured models can be useful surrogates for demographic models when the goal is to estimate or forecast population states over large spatial extents.
Likewise, the equivalency of forecast accuracy between the IPM and QBM held for all four species, when climate covariates are not included, extending the generality of previous findings [e.g., @Taylor2004; @Queenborough2011]. THIS LAST SENTENCE SEEM REDUNDANT WITH PREVIOUS SENTENCES...AM I MISSING SOMETHING? COMBINE?

@@

The higher accuracy of the IPM with climate covariates for *P. secunda*  highlights the advantage of contemporary model and variable selection approaches such as ridge regression and LASSO over techniques that would exclude "non-significant" effects from final models.
Especially in a Bayesian forecasting framework, ridge regression allows researchers to include forcing variables that we know are changing (e.g., temperature and precipitation) in final models even if the estimated effects are relatively small or even deemed unimportant due to noisy data, out of which it is more difficult to estimate effects on interannual variation [REWERITE THIS SENTENCE, I DON'T KNOW HOW TO RESCUE IT CUZ I DON'T UNDERSTAND IT].
Likewise, if a species is truly unresponsive to a given climate variable, statistical regularization techniques will shrink the mean and variance of a covariate estimate to zero [@Hooten2015].
Of course, no matter what model selection approach is adopted, a critical step is identifying the appropriate candidate covariates, which we attempted to do based on our knowledge of this semi-arid plant community.
However, the climate covariates we chose required aggregating daily weather data over discrete time periods.
It is possible that we did not choose the optimal time periods over which to aggregate.
New methods using functional linear models (or splines) may offer a data-driven approach for identifying the appropriate time periods over which to aggregate to produce a tractable set of candidate climate variables [@Teller2016].

@@

In conclusion, we found that models based on individual-level demographic data generally failed to generate more skillful population forecasts than models based on population-level data.
This finding runs counter to our expectations, but is consistent with recent theoretical [@Freckleton2011] and empirical work [@Queenborough2011].
However, when we included climate covariates, we did achieve more skillful forecasts from the IPM for one species, *P. secunda*, that appears to respond consistently, but weakly, to several climate variables [THIS SENTENCE NEEDS WORK, BUT I AM GOING TO BED].
Thus, we conclude that models based on population-level data, rather than individual-level data, may be adequate for forecasting the state of plant populations for species that do not respond consistently or strongly to climate.
Unfortunately, our analysis, where climate effects were relatively unimportant in vital rate regressions, did not allow us to sufficiently test our prediction that individual-level data is neccessary to generate skillful forecasts if different vital rates respond to climate in unique, potenially opposing, ways.
Nonetheless, our results are encouraging for the use of easy-to-collect percent cover for forecasting the state of plant populations.

IS THE REST OLD? I STOPPED HERE.

<!---
### The importance of demographic data
Our comparison of a traditional, demographic population model (the IPM) with a model inspired by density-structured models (the QBM) showed that the IPM outperformed the QBM: the IPM was more accurate and precise than the QBM in out-of-sample cross validation (Table 1). The superiority of the IPM could reflect either differences in sample size or the effect of averaging over unique effects of climate on each individual-level vital rate. Although increasing sample size of quadrat percent-cover observations would be easy to do in the field, we found little evidence that it would lead to higher precision of climate coefficient estimates (Fig. 4).

We did, however, find evidence that the QBM statistical model failed to identify climate dependence for some vital rates (Fig. 5). For no species were climate effects from the QBM strongly correlated with all three vital rates (Fig. 5). @Freckleton2011 acknowledge that averaging over complex stage dependence will lead to poorly specified models. This is analagous to our situation, but instead of averaging over complex life histories, we are averaging over complex climate dependence. Though our work here focused on plant species, this finding is applicable to any species with vital rates that respond uniquely to weather/climate.

Our interpretation is that the QBM is "missing" climate signals associated with at least one vital rate for each species. This leads to inaccurate and imprecise forecasts because the QBM statistical model struggles to explain variation due to climate variables that have positive and negative impacts on different vital rates. When this is the case, as it is for all our species to varying degrees (Fig. 3), forecasts from models based on population-level data will fail. Our result is consistent with related work on the importance of individual-level data to forecast population responses to exogenous drivers [@Clark2011; @Clark2011b; @Clark2012; @Galvan2014].

Detailed demographic data appears to be necessary to forecast climate change impacts on plant populations when vital rates have unique climate responses. How then can we build models to make forecasts for the landscape and regional scales beyond the scope of traditional population models [@Queenborough2011]? There are alternatives to density-structured models. For example, @Clark2011 use Forest Inventory and Analysis (FIA) data to parameterize a population model with multiple vital rates and climate dependence. Distributed efforts such as PlantPopNet (http://plantago.plantpopnet.com) will allow researchers to estimate variation around climate responses for widespread species by taking advantage of spatial variation in climate [e.g. @Doak2010]. Finally, new approaches on the horizon that leverage photo/video of plots and advanced object recognition algorithms [e.g. @Liu2014] will increase the efficiency of plant mapping and digitizing efforts.

### The challenge of uncertainty

An important, but unexpected, result of our analysis was the great uncertainty in forecasts, even for our best model. The typical approach in ecology is to use point estimates of model parameters to project populations forward according to the specified model, usually allowing for some variability around the determinstic process [e.g. @Battin2007; @Jenouvrier2009; @Adler2012]. If we follow tradition and calculate the mean response to climate perturbation with only model error and interannual variation included, the IPM and the QBM produce opposing forecasts for three of four species (Fig. D1). It would be tempting to interpret this inconsistency as further evidence for the superiority of the IPM. However, if we introduce parameter uncertainty, the forecasts are actually indistinguishable (Fig. 6), though the IPM projections are generally more precise (consistent with our cross-validation results). The real story is that both models produce highly uncertain forecasts. For all species, the 90% quantiles of predicted changes in population size overlapped zero; we cannot even predict whether a change in precipitation or temperature will cause populations to increase or decrease. This result held when we tried perturbing climate by 10% and 20% as well.

Our results highlight the state of affairs in ecology when it comes to forecasting the impacts of climate change. The analysis we conducted here could be considered at the forefront of ecological forecasting with respect to the statistical approach employed (hierarchical Bayesian), the type of population model we used (density-dependent, stochastic IPM with parameter uncertainty), and the amount of high quality data we had at our disposal (14 years of individual-level data). Yet, model predictions proved so uncertain that any forecast, when bounded with model and parameter uncertainty, would be uninformative.

How might we improve on this state of affairs? First, forecasts could be improved by matching the spatial scale of predictor variables with the spatial scale of observations. One of the major limitations of the models we fit here is that the climate data are collected at a larger scale than the individual-level observations of plant size. Climate covariates only vary by year, with no spatial variability within years. Thus, even if we fit models to individual-level data, we are missing the key interaction point between weather and individual plants [@Clark2011b] because all observations share the same climate covariates. Demographic studies should be designed with at least plot-level measurements of climate related variables (e.g., soil moisture). Second, accurately detecting climate signals will take even longer time series. Recent theoretical work on detecting climate signals in noisy data suggests that even advanced approaches to parameter fitting require 20-25 year time series [@Teller2016]. Third, ecologists need a stronger commitment to reporting uncertainty. Although most modeling studies explicitly consider model uncertainty, parameter uncertainty is often ignored. In some cases this is because the most convenient statistical methods make it difficult to propogate parameter uncertainty. Yet even Bayesian approaches that allow integration of model fitting and forecasting [@Hobbs2015] are not simple when using modeling approaches like integral projection models that separate the model fitting and simulation stages [@Rees2009]. However, as we have done here, it is still possible to include parameter uncertainty by drawing parameter values from MCMC iterations, taking care to draw all parameters from the same chain and iteration to account for their correlations. Only by being honest about our forecasts can we begin to produce better ones, and forecasts reported without parameter error are disingenuous.  Ignoring parameter error may be justifiable when the goal is investigating basic processes, but it is indefensible when forecasting is the goal.

Conclusions
-----------
This work is not a critique of density-structured population models. We are confident that density-structured models will prove to be a valuable tool for many applications. However, our analysis represents the first comparison, to our knowledge, of population models based on individual and aggregated forms of the same data in a climate change context. Our results confirm theoretical arguments [@Clark2011b] and empirical evidence [@Clark2011; @Clark2012] that individual responses are critical for predicting species' responses to climate change. It seems there is no short cut to producing accurate and precise population forecasts: we need detailed demographic data to forecast the impacts of climate change on populations. Given the importance of demographic data and its current collection cost, we need modern methods to collect demographic data more efficiently across environmental gradients in space and time.

Our results also offer a cautionary tale because forecast uncertainty was large for both model types. Even with 14 years of detailed demographic data and sophisticated modeling techniques, our projections contained too much uncertainty to be informative. Uncertainty in demographic responses to climate can be reduced by collecting (1) longer time series and (2) climate covariates that match the scale of inference (e.g., plot rather than landscape level climate/weather metrics). 
--->

@@

Tables
------
\begin{table}[ht]
\centering
\caption{Description of data.} 
\begin{tabular}{llrr}
  \hline
Species & Vital Rate Model & Num. Obs. & Num. Quadrats\\ 
  \hline
  \emph{B. gracilis} & Growth & 5670 & 29 \\ 
       & Survival & 10102 & 33 \\ 
       & Recruitment & 304 & 33 \\ 
       & Percent cover & 281 & 29 \\ 
  \rule{0pt}{3ex} \emph{H. comata} & Growth & 1990 & 16 \\ 
       & Survival & 3257 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 171 & 17 \\ 
  \rule{0pt}{3ex} \emph{P. smithii} & Growth & 8052 & 19 \\ 
       & Survival & 11344 & 19 \\ 
       & Recruitment & 304 & 19 \\ 
       & Percent cover & 217 & 19 \\ 
  \rule{0pt}{3ex} \emph{P. secunda} & Growth & 3018 & 18 \\ 
       & Survival & 4650 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 197 & 18 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

**5.** *Synthesis.* For our focal species at this particular location, and using our particular statistical models, percent cover models generated forecasts as skillful as those from a demographic model.
However, for certain species forecast skill can be gained by using demographic data linked to climate covariates.
We conclude that models based on aggregated individual-level data offer a practical alternative to data-intensive demographic models when species do not respond strongly to interannual variation in weather, but when modeling species that do respond to climate drivers, demographically-based models can generate more skillful forecasts.

@@

@@

Addressing climate change questions with models fit to population-level data is potentially problematic. Population growth (or decline) is the outcome of demographic processes such as survival, growth, and recruitment that occur at the level of individual plants. Climate can affect each demographic process in unique, potentially opposing, ways [@Dalgleish2011]. These unique climate responses may be difficult to resolve in statistical models based on population-level data where demographic processes are not identifiable. Futhermore, models based on aggregated data may reflect short-term effects of one vital rate more than others whose importance may only emerge over the long-term. For example, a one-year change in a plant species' cover or biomass might reflect individual growth or shrinkage, whereas the long-term trajectory of the population might be more influenced by recruitment. The same is true for density dependence: intraspecific density depedence may act most strongly on vital rates, like recruitment, that are difficult to identify from population-level data. If density dependence and/or important climate effects are missed because of the aggregation inherent in in population-level data, then population models built with such data will make uninformative or unreliable forecasts.

Here, we compare the forecasting skill of statistical and population models based on aggregated, population-level data with the skill of models based on individual-level data. We used a demographic dataset that tracks the fates of individual plants from four species over 14 years to build two kinds of single-species population models, traditional models using individual growth, survival, and recruitment data and alternative models based on basal cover. We simulated the models to answer two questions motivated by the fact that the effects of intraspecific competition (density dependence) and interannual weather variability act at the level of the individual [@Clark2011b].
First, can population models fit using aggregated individual-level data (percent cover) adequately capture density dependence to produce forecasts as skillful as those from models fit to demographic data? 
Second, can population models fit using aggregated data adequately capture the influence of climate on population growth and, in turn, produce forecasts as skillful as those from models fit to demographic data?

@@

We follow the approach of @Chu2015 to estimate crowding, assuming that the crowding experienced by a focal genet depends on distance to each neighbor genet and the neighbor's size, _u_:

\begin{equation}
w_{i,t} = \sum_k e^{-\deltad_{ik,t}^{2}}u_{k,t}.
\end{equation}

In the above, $w_{i,t}$ is the crowding that genet _i_ in year _t_ experiences from conspecific neighbors. The spatial scale over which conspecific neighbors exert influence on any genet is determined by $\delta$. The function is applied for all _k_ conspecific genets that neighbor the focal genet at time _t_, and $d_{ik,t}$ is the distance between genet _i_ and conspecific genet _k_. We use regression-specific (survival and growth) $\delta$ values estimated by @Chu2015.

@@

This cross-validation procedure allowed us to compare accuracy and precision of the two modeling approaches (IPM versus QBM) with and without climate covariates. We first calculated the median predicted cover across the 100 simulations for each quadrat-year and then calculated forecast skill as the correlation ($\rho$) between forecasts and observations. We calculated forecast error as mean absolute error (MAE) between forecasts and observations. We compared $\rho$ and MAE between model types and within model types between models with and without climate covariates using one-sided *t* tests with adjusted degrees of freedom following @Wilcox2009 and standard errors calculated using the HC4 estimator of @Cribari-Neto2004. Statistical tests for differences between $\rho$ were conducted using R functions from @Ye2015a.

@@

Results
-------
The IPM and QBM generated one-step-ahead forecasts of similar skill for out-of-sample observations, with an average correlation between predictions and observations ($\rho$) of 0.73 across all models and species (Fig. 2).
Without climate covariates, the accuracy of forecasts from the IPM were not statistically greater than the accuracy of forecasts from the QBM (Fig. 2) and overall error was similar (mean absolute error; Fig. S1).
With climate covariates, the best out-of-sample predictive model (highest *lppd*) for each species and vital rate typically resulted from highly constrained priors on the climate effects (Fig. S2).
Thus, the posterior distributions of climate effects included in our models overlapped zero and generally shrunk toward zero, though for some species-vital rate combinations important effects (80% credible interval does not include zero) did emerge (Fig. 3).

Despite the weak climate effects, including climate covariates did increase the accuracy of forecasts for all species except *P. smithii* (Fig. 2).
Increases in accuracy due to the inclusion of climate covariates were not significant (*P* > 0.05 for all comparisons of $\rho$ between climate and no-climate forecasts within model types; Fig. 2).
However, the IPM with climate covariates for *P. secunda* did have significantly lower error (mean absolute error) than the IPM without climate covariates ($t_{(196)}$ = -1.84, *P* = 0.033; Fig. S2).
In only one case were IPM forecasts significantly more accurate than the QBM (Fig. 2): forecast accuracy of *P. secunda* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(195)}$ = 1.72, *P* = 0.043).
Forecasts from IPMs with climate covariates had significantly lower error than equivalent QBM forecasts for *P. smithii* ($t_{(216)}$ = -3.49, *P* < 0.001) and *P. secunda* ($t_{(196)}$ = -1.83, *P* = 0.034) (Fig. S2).
Results from all pairwise statistical tests are shown in Table S1.

The accuracy of both model's forecasts declined as the forecast horizon increased, but they did so at similar rates (Fig. 4).
The only exception is for *P. secunda* where forecast accuracy appears to remain steady as the forecast horizon increases, after an initial decrease from a forecast horizon of one year (Fig. 4).

@@

Our comparison of a traditional, demographic population model without environmental forcing (the IPM) to an equivalent model inspired by density-structured models (the QBM) showed that, generally, IPM forecasts of out-of-sample plant population states were no more accurate than forecasts from the QBM (Fig. 2; `no-climate' bars).
We expected the IPM to out-perform the QBM since the IPM includes more mechanistic detail on the perennial plant life cycle, but this was not the case, at least when we ignored environmental forcing.
Such a finding confirms theoretical [@Freckleton2011] and empirical work [@Taylor2004; @Queenborough2011] showing that density-structured models can be useful surrogates for demographic models when the goal is to estimate or forecast population states over large spatial extents.

@@

The higher accuracy of the IPM with climate covariates for *P. secunda*  highlights the advantage of contemporary model and variable selection approaches such as ridge regression and LASSO over techniques that would exclude "non-significant" effects from final models.
Ridge regression allows researchers to retain covariates whose effects may be difficult to identify in noisy data or short time series.
This is especially important when forecasting the impacts of climate change where it is important to include to effects of forcing variables (e.g., temperature and precipitation) even of such effects are difficult to identify.
If a species is truly unresponsive to a given climate variable, statistical regularization techniques will shrink the mean and variance of a covariate estimate to zero [@Hooten2015].
Of course, no matter what model selection approach is adopted, a critical step is identifying the appropriate candidate covariates, which we attempted to do based on our knowledge of this semi-arid plant community.
However, the climate covariates we chose required aggregating daily weather data over discrete time periods.
It is possible that we did not choose the optimal time periods over which to aggregate.
New methods using functional linear models (or splines) may offer a data-driven approach for identifying the appropriate time periods over which to aggregate to produce a tractable set of candidate climate variables [@Teller2016].

@@

In conclusion, we found that models based on individual-level demographic data generally failed to generate more skillful population forecasts than models based on population-level data.
This finding runs counter to our expectations, but is consistent with recent theoretical [@Freckleton2011] and empirical work [@Queenborough2011].
However, we did achieve more skillful forecasts from the IPM with climate covariates for one species, *Poa secunda*, that appears to respond consistently to several climate variables.
Thus, we conclude that models based on population-level data, rather than individual-level data, may be adequate for forecasting the state of plant populations for species that do not respond consistently or strongly to climate.
Unfortunately, our analysis, where climate effects were relatively unimportant in vital rate regressions, did not allow us to sufficiently test our prediction that individual-level data is neccessary to generate skillful forecasts if different vital rates respond to climate in unique, potenially opposing, ways.
Nonetheless, our results are encouraging for the use of easy-to-collect percent cover for forecasting the state of plant populations.

@@

Tables
------
\begin{table}[ht]
\centering
\caption{Description of data. The observations span 13 year-to-year transitions.} 
\begin{tabular}{llrr}
  \hline
Species & Vital Rate Model & Num. Obs. & Num. Quadrats\\ 
  \hline
  \emph{B. gracilis} & Growth & 5670 & 29 \\ 
       & Survival & 10102 & 33 \\ 
       & Recruitment & 304 & 33 \\ 
       & Percent cover & 281 & 29 \\ 
  \rule{0pt}{3ex} \emph{H. comata} & Growth & 1990 & 16 \\ 
       & Survival & 3257 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 171 & 17 \\ 
  \rule{0pt}{3ex} \emph{P. smithii} & Growth & 8052 & 19 \\ 
       & Survival & 11344 & 19 \\ 
       & Recruitment & 304 & 19 \\ 
       & Percent cover & 217 & 19 \\ 
  \rule{0pt}{3ex} \emph{P. secunda} & Growth & 3018 & 18 \\ 
       & Survival & 4650 & 18 \\ 
       & Recruitment & 304 & 18 \\ 
       & Percent cover & 197 & 18 \\ 
   \hline
\end{tabular}
\end{table}
